---
title: "Total Recall"
author: Kyle Kurkela
output:
  github_document:
    html_preview: false
---

```{r setup, echo=FALSE, warning=FALSE, message=FALSE}
library('tidyverse')
```

# Read it in

```{r}
datapath <- '/Users/kylekurkela/Google Drive/Experiments/TOTAL RECALL/Data/'
datafiles.study <- list.files(datapath,pattern='.*study.*', full.names=TRUE, recursive=TRUE)
df.study <- do.call(rbind, lapply(datafiles.study, read.csv))
```

# Total time

Below is a table of the maximum onset time relative to the start of the experiment for each subject. This gives us a rough idea of how much time people are taking the entire experiment as currently designed.  

```{r}
df.study %>%
  group_by(subjectID) %>%
  summarise(maxOnset = max(ExpOnset) / 60)
```

# Time for each list

Below is the average time it takes pariticpants to complete a list. Each participants completes a total of 16 lists. Each additional list will add an additional ~2.38 seconds onto the length of the experiment.  

```{r}
df.study %>%
  group_by(subjectID, listID) %>%
  summarise(maxOnset = (max(ListOnset) + 75) / 60) %>%
  ungroup() %>%
  summarize(average_time_to_complete_a_list = mean(maxOnset)) %>%
  print()
```

