---
title: "TOTO-tDCS"
author: "Kyle Kurkela"
output: 
  html_notebook: 
    code_folding: hide
    toc: yes
    toc_float: yes
---

Welcome to the `TOTO-tDCS` ~~jupyter Notebook~~ R Markdown!

Today we will be presenting the results of the [Memory Modulation Lab](http://www.thememolab.org/)'s `TOTO-tDCS` experiment, analyzed using [Quail](http://cdl-quail.readthedocs.io/en/latest/) and Python 2.7 and plotted using everyone's favorite statistical ecosystem the tidyverse (<3).

# Load in libraries

Let us begin be importing the R packages and python modules we will be using.

```{r setup, warning=FALSE, message=FALSE}
# reticulate is the R package that allows the transitions between R <--> python
library('reticulate')
use_condaenv(condaenv = "py2716", conda = "/anaconda3/bin/conda")
py_config()
# <3
library('tidyverse')
 
library('googlesheets')

library('scales')

library('ez')
```

```{python import}
import glob # for matching filenames using wildcards
import re # regular expressions
import pandas as pd # a tidyverse esq python data manipulation package
import quail as q # andy's free recall package
import numpy as np # arrary manipulation
import math
from scipy import stats # python statistics
import os
```

# Read in Data

Next, lets read in the `TOTO-tDCS` data.

We will read in the data (currently as .tsv (study) and .csv (recall) files) using pandas' `read_csv` method.

## Study

First, the study phase.

NOTES: 
- s004 fell asleep  
- s025 dropped out of the study  

```{r read_and_extract_study}
# a custom function for reading in the delimitted study data files, extracting the sessionID from the file names.
custom.read.delim <- function(a){
  tmp <- read.delim(a)
  sessionID <- regmatches(x = a, m = regexpr(text = a, pattern = "ses-[0-9]{2}"))
  tmp <- add_column(tmp, sessionID)
  return(tmp)
}
 
# hardcoded path, list all files recursively from that path, 
# read the files in, and bind it all up into a single data.frame
files  <- list.files(path = "/Volumes/GoogleDrive/My Drive/Behavioral Data/TOTO-tDCS/", 
                     recursive = TRUE, 
                     pattern = "sub-s[0-9]{3}.*\\.tsv", 
                     full.names = TRUE)
study  <- lapply(files, custom.read.delim)
study  <- do.call(rbind, study)
 
# arrange the study data frame in a specific order. Important later on for the quail package.
study %>%
  arrange(sessionID, subjectID, Condition, listID, ListOnset) %>%
  filter(!is.element(set = c("s004", "s025"), el = subjectID))-> study
```

## Test

Second, the test phase.

```{r read_and_extract_test, warning=FALSE}
# Defining a custom read csv function, which extracts the sessionID, subjectID, and listID from the filenames
custom.read.csv <- function(a){
  
  # read
  tmp <- read.csv(a, blank.lines.skip = FALSE)
  
  # extract
  sessionID <- regmatches(x = a, m = regexpr(text = a, pattern = "ses-[0-9]{2}"))
  subjectID <- regmatches(x = a, m = regexpr(text = a, pattern = "(?<=sub-)s[0-9]{3}", perl = TRUE))
  listID    <- regmatches(x = a, m = regexpr(text = a, pattern = "(?<=list-)[0-9]{2}", perl = TRUE))
  
  if (is_empty(tmp[[1]])){ # if file is empty
    emily <- "emptyFile"
    tmp   <- add_column(tmp, emily, sessionID, subjectID, listID)
    tmp   <- add_row(tmp, 
                     emily = emily, 
                     sessionID = sessionID, 
                     subjectID = subjectID, 
                     listID = listID)
  } else if(!is.element("emily", colnames(tmp))){ # if there isn't an Emily column
    emily <- "noEmilyColumn"
    tmp   <- add_column(tmp, emily, sessionID, subjectID, listID)
  } else { # otherwise
    tmp   <- add_column(tmp, sessionID, subjectID, listID)
  }
  
  return(tmp)
  
}
 
# hardcoded path, list all files recursively from that path, 
# read the files in, select only the necessary columns, 
# and bind it all up into a single data.frame
files <- list.files(path = "/Volumes/GoogleDrive/My Drive/Behavioral Data/TOTO-tDCS/", 
                    recursive = TRUE, 
                    pattern = "sub-s[0-9]{3}.*\\.csv", 
                    full.names = TRUE)
recall  <- lapply(files, custom.read.csv)
recall  <- lapply(recall, select_, "emily", "sessionID", "subjectID", "listID")
recall  <- do.call(rbind, recall) %>%
           mutate(listID = as.integer(listID))
```

# Prepare data

The `Quail` python package needs the data to be arranged in a very specific way. The data need to be arranged as a list of lists, each outer list containing all the of the lists for a subject and each inner list all of the words for a specific list.

## Study

```{python dataframe_to_list_of_lists}
# Goal: turn `study` data.frame into a lists of lists
 
# initialize two variables `presented_words` and `presented_word_features`, 
# which will be used to create the egg.
presented_words = []
presented_word_features = []
 
# for each subject...
for s in r.study['subjectID'].unique():

    # all of the data related to the current subject
    cur_sub = r.study[r.study['subjectID'] == s]
    
    # initalizing temporary variables to hold the words 
    # on this list and the features of the words on this list
    lists = []
    lists_features = []
    
    for ses in cur_sub['sessionID'].unique():
    
      cur_sub_cur_ses = cur_sub[cur_sub['sessionID'] == ses]
  
      # for each list...
      for l in cur_sub_cur_ses['listID'].unique():
      
          # current list subset of cur_sub_cur_ses data.frame
          cur_list = cur_sub_cur_ses[cur_sub_cur_ses['listID'] == l]
  
          # the words presented on this list
          words = list(cur_list['Word'])
  
          # force lowercase
          words = map(str.lower, words)
  
          # append
          lists.append(words)
          lists_features.append(cur_list[['EmotionCategory']].to_dict(orient='records'))
 
    # append
    presented_words.append(lists)
    presented_word_features.append(lists_features)
```

## Test

```{python}
# Goal: turn `recall` data.frame into a lists of lists. 
# Note: must match the order of the `study` data.frame

# initalize a list of recalled words
recalled_words = []

# for each subject...
for s in r.study['subjectID'].unique():
    
    # the current subject's encoding (or study) data
    cur_sub = r.study[r.study['subjectID'] == s]
    
    # initialize a temporary variable to hold the recalled words
    lists = []
    
    for ses in cur_sub['sessionID'].unique():
    
        # current subject current sessionID
        cur_sub_cur_ses = cur_sub[cur_sub['sessionID'] == ses]
    
        # for each list from **encoding/study**...
        for l in cur_sub_cur_ses['listID'].unique():
        
            # the current list from **recall**
            cur_list = r.recall[np.array(r.recall['listID'] == l) & np.array(r.recall['subjectID'] == s) & np.array(r.recall['sessionID'] == ses)]
    
            # words recalled from this list for this subject
            words = cur_list.iloc[:, 0].tolist()
    
            # remove tildes (~) in words
            while '~' in words:
                words.remove('~')
    
            # remove question marks (?) in words
            while '?' in words:
                words.remove('?')
                
            if words == "emptyFile":
                words = []
    
            # remove nans
            c = -1
            for w in words:
                c = c + 1            
                if type(w) != str:
                    words[c] = ''
    
            # strip leading and trailing white space
            c = -1
            for w in words:
                c = c + 1            
                words[c] = words[c].strip()
    
            # force the words to be lowercase and append
            lists.append(map(str.lower, words))

    # append
    recalled_words.append(lists)
```

# Eggs!

Lets create our `egg`, the variable used in the quail package.

```{python}
# create an egg
egg = q.Egg(pres=presented_words, rec=recalled_words, features=presented_word_features)

# information about the egg
egg.info()
```

# Demographics

Who were our participants?

```{r}
require('googlesheets')
```

```{r warning=FALSE, message=FALSE}
# Grab the participant information questionnaire
participant_info_gsheet <- gs_title("Participant Information Questionnaire")
participant_info_df     <- gs_read(participant_info_gsheet, range = "A1:N26", progress = FALSE)
 
# clean it up a bit
participant_info_df %>%
 filter(!is.element(set = c("s004", "s025"), el = subject)) %>%
 select(age, gender, education, sleep, stress) -> participant_info_df
 
# Numeric Data
participant_info_df %>%
  summarise_if(is.numeric, c('mean', 'sd'), na.rm = TRUE)

# Catergorical Data
participant_info_df %>%
  count(gender)
```


# Accuracy

Below are the two lines needed to calculate recall accuracy in the quail package.

```{python}
recall_accuracy = q.analyze(egg, analysis='accuracy')
recall_accuracy.reset_index(inplace=True)
```

## Subject Summary

How did participants do overall?

Below is a table displaying ALL OF THE DATA. I.e., how every participant performed on every list.  

```{r plot_in_ggplot, warning=FALSE}
(py$recall_accuracy %>%
  mutate(sessionID = if_else(condition = is.element(set = seq(0,15,1), el = List), 
                             true = "ses-01", 
                             false = "ses-02"),
         Condition = if_else(condition = is.element(set = c(seq(0,7,1), seq(16,23,1)), el = List), 
                             true = "allNeutral", 
                             false = "halfEmotional")) %>%
  rename(proportion = `0`) %>%
  mutate(Subject = rep(unique(as.character(study$subjectID)), each = 32)) -> d.f)
```

A visual summary:

```{r}
# Base Plot
d.f %>%
  ggplot(aes(x = Subject, y = proportion, fill = Subject)) +
    theme_grey() +
    theme(panel.grid.major = element_blank(), 
          panel.grid.minor = element_blank()) +
    scale_y_continuous(limits = c(0,1), 
                       labels = c("0%", "25%", "50%", "75%", "100%"), 
                       name = "Proportion Recalled") -> Base

# By Subject
Base +
  stat_summary(geom = "bar", 
               position = position_dodge(width = .9), 
               width = .5, 
               fun.data = "mean_se") +
  stat_summary(geom = "errorbar", 
               width = .2, 
               position = position_dodge(width = .9), 
               fun.data = "mean_se") +
  geom_hline(yintercept = mean(d.f$proportion), color = "red") +
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Proportion Recalled", 
      subtitle = "By Subject",
      caption = "Red Line = Overall Mean") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


Participants recalled, on average, a little over 50% of the words with performance ranging from min = ~25% to max = ~87%. This looks like a nice grand mean, far away from the floor and ceiling. There should be enough room for our conditions to push the proportions around nicely.  

## Session Order

Does session order matter? Did participants do better in the second session than the first?

```{r by_session, warning=FALSE}
d.f %>%
  group_by(Subject, sessionID) %>%
  summarise(proportion = mean(proportion)) %>%
  t.test(proportion ~ sessionID, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 2)

Base +
  aes(x = sessionID, fill = NULL, color = sessionID) +
  stat_summary_bin(aes(group = Subject), geom = "line", fun.y = "mean") +
  stat_summary_bin(aes(group = Subject), geom = "point", fun.y = "mean") +
  stat_summary(geom = "crossbar", fun.data = "mean_se", width = .1) +  
  annotate(geom = "text", x = 1.5, y = 1, label = paste0("t(", df, ") =", t, ", p = ", p)) +
  scale_fill_discrete(guide = FALSE) +
  scale_x_discrete(labels = c("01", "02")) +
  labs(title = "Proportion Recalled",
        subtitle = "By Session",
        x = "Session")
```

Participants seemed to do slightly better in session 2 than in session 1, although this effect is not statistically significant.  

## Condition

Did participants recall different numbers of words from the `allNeutral` lists than the `halfEmotional` lists?

The `allNeutral` condition were recall lists made up entirely of neutral words (as operationalized by Long et al., 2015).
The `halfEmotional` condition were recall lists made up of halfEmotional words (as operationalized by Long et al., 2015).

```{r by_condition, warning=FALSE}
d.f %>%
  group_by(Subject, Condition) %>%
  summarise(proportion = mean(proportion)) %>%
  t.test(proportion ~ Condition, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 2)

Base +
  stat_summary_bin(aes(x = Condition, group = Subject, fill = NULL), 
                   geom = "point", 
                   fun.y = "mean") + 
  stat_summary_bin(aes(x = Condition, group = Subject, fill = NULL), 
                   geom = "line", 
                   fun.y = "mean") +
  stat_summary(aes(x = Condition, color = Condition, fill = NULL), geom = "crossbar", width = .2, fun.data = "mean_se") +
  annotate(geom = "text", x = 1.5, y = 1, label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +  
  labs(title = "Proportion Recalled",
        subtitle = "By Condition",
        x = "Condition")
```

There seemes to be a trend for a slighly greater number of words remembered in the `halfEmotional` lists, but, again, the result is not statistically significant.  

## Protocol

Drum roll...is there an overall effect of the Protocol? Does stimulation have any effect over sham?  

Below is the meta data on the sessions. Note: Stimulation Protocol was counerbalanced.  

```{r grab_subjectIDs_googlesheet, message=FALSE, warning=FALSE}
# Grab the subject IDs google sheets
subjectIDs_gsheet <- gs_title("TOTO-tDCS_SubjectIDs")
subjectIDs_df     <- gs_read(subjectIDs_gsheet, range = "A11:I85", progress = FALSE)
 
# clean it up a bit
(subjectIDs_df %>%
  filter(!is.na(Date)) %>% # remove the NA rows, indicative of subjects not yet collected
  slice(2:n()) %>% # remove the first row
  select(SubjectID, Session, StimulationProtocolID, TimeOfDay) %>% # only need these columns for the present purposes
  mutate(Session = if_else(Session == 1, "ses-01", "ses-02")) %>%
  filter(SubjectID != "s034 take 1") %>%
  mutate(SubjectID = gsub(pattern = " take 2", replacement = "", x = SubjectID)) -> subjectIDs_df)
```

A visual:  

```{r}
# Combine
d.f <- left_join(d.f, subjectIDs_df, by = c("Subject" = "SubjectID", "sessionID" = "Session"))

# stats
d.f %>%
  group_by(Subject, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion)) %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 2)

# plot!
d.f %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, group = Subject, color = StimulationProtocolID)) +
  stat_summary_bin(geom = "point", fun.y = "mean") + 
  stat_summary_bin(geom = "line", fun.y = "mean") +
  stat_summary(aes(group = NULL), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  scale_y_continuous(limits = c(0,1), 
                     labels = c("0%", "25%", "50%", "75%", "100%"), 
                     name = "Proportion Recalled") +
  theme_grey() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(title = "Proportion Recalled",
        subtitle = "By Protocol",
        x = "Condition")
```

Numerically, pariticpants tended to remember more words in protocol A than in protocol B. The result, however, was not statistically significant. 

# Temporal Contiguity

Did stimulation influence the Temporal Contiguity Phenomenon?  

First, lets calculate it in python using `Quail`.  

```{python}
temporal = q.analyze(egg, analysis='temporal')
temporal.reset_index(inplace=True)
```

Read into R and clean up a bit.  

```{r}
(py$temporal %>%
  mutate(sessionID = if_else(condition = is.element(set = seq(0,15,1), el = List), 
                             true = "ses-01", 
                             false = "ses-02"),
         Condition = if_else(condition = is.element(set = c(seq(0,7,1), seq(16,23,1)), el = List), 
                             true = "allNeutral", 
                             false = "halfEmotional")) %>%
  rename(proportion = `0`) %>%
  mutate(Subject = rep(unique(as.character(study$subjectID)), each = 32)) -> d.f.temporal)
```

## Subject Overview

What does the temporal contiguity effect look like across participants?

```{r, warning = FALSE}
d.f.temporal %>%
  ggplot(aes(x = Subject, y = proportion, fill = Subject)) +
  stat_summary(geom = "bar", position = position_dodge(width = .9), width = .5, fun.data = "mean_se") +
  stat_summary(geom = "errorbar", width = .2, position = position_dodge(width = .9), fun.data = "mean_se") +
  geom_hline(yintercept = mean(d.f.temporal$proportion, na.rm = TRUE), color = "red") +
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Temporal Contiguity", 
      subtitle = "By Subject",
      caption = "Red Line = Overall Mean\ns004 and s025 dropped out of the study") + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  scale_y_continuous(limits=c(.5, 1), oob = rescale_none)
```

Note: a score of "1" would indicate perfect temporal contiguity. In other words, a participant *always* remembered words in temporal sequence. A score of .5 indicates a complete absence of temporal contiguity: there was absolutely no evidence of a tendency to recall words successively.  

## Session Order

Does temporal contiguity differ by session? Do participants tend to change the temporal clustering in the second session?

```{r warning=FALSE}
# stats
d.f.temporal %>%
  group_by(Subject, sessionID) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  t.test(proportion ~ sessionID, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 3)

# plot!
d.f.temporal %>%
  ggplot(aes(x = sessionID, y = proportion, group = Subject, color = sessionID)) +
  stat_summary_bin(geom = "point", fun.y = "mean") +
  stat_summary_bin(geom = "line", fun.y = "mean") +
  stat_summary(aes(group = NULL), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  scale_y_continuous(name = "Temporal Contiguity Score") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(title = "Temporal Contiguity",
        subtitle = "By Session",
        x = "Session Order")
```

Participants displayed signifcantly more temporal clustering in `ses-02` than in `ses-01`. I hypotheses that this result reflects participants learning a strategy implemented at encoding to assist remembering words in termporal order. For example: creating a story linking the words together in the order that they appeared.  

## Condition

```{r warning=FALSE}
# stats
d.f.temporal %>%
  group_by(Subject, Condition) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  t.test(proportion ~ Condition, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 2)

# plot!
d.f.temporal %>%
  ggplot(aes(x = Condition, y = proportion, group = Subject, color = Condition)) +
  stat_summary_bin(geom = "point", 
                   fun.y = "mean") +
  stat_summary_bin(geom = "line", 
                   fun.y = "mean") +
  stat_summary(aes(group = NULL), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  scale_y_continuous(name = "Temporal Contiguity Score") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(title = "Temporal Contiguity",
       subtitle = "By Condition",
       x = "Condition")
```

There appears to be no difference in temporal contiguity by Valence condition.  

## Protocol

Is there an effect of protocol?!?!

```{r, warning=FALSE}
# combine
d.f.temporal <- left_join(d.f.temporal, subjectIDs_df, by = c("Subject" = "SubjectID", "sessionID" = "Session"))

# stats
d.f.temporal %>%
  group_by(Subject, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 2)

# plot!
d.f.temporal %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, group = Subject, color = StimulationProtocolID)) +
  stat_summary_bin(geom = "point", fun.y = "mean") + 
  stat_summary_bin(geom = "line", fun.y = "mean") +
  stat_summary(aes(group = NULL), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  labs(title = "Temporal Contiguity",
       subtitle = "By Protocol",
       x = "Protocol")
```

...no, unfortunetly not. :(

What is the distribution of temporal contiguity scores for each subject?

```{r}
for(s in d.f.temporal$Subject){
}
d.f.temporal %>%
  filter(Subject == "s001") %>%
  ggplot(aes(x=proportion, fill=interaction(Condition, StimulationProtocolID))) +
  geom_histogram(binwidth = .1, alpha=.5, position="identity")
```


Full ANOVA

```{r, warning=FALSE,message=FALSE}
require('ez')
d.f.temporal %>%
  filter(Subject != "s020") %>%
  group_by(Subject, StimulationProtocolID, Condition) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  ezANOVA(
    data = .,
    dv = proportion,
    within = .(Condition, StimulationProtocolID),
    wid = Subject,
    detailed = TRUE,
    return_aov = TRUE
  ) -> temporal.ANOVA
print(temporal.ANOVA$ANOVA)
model.tables(temporal.ANOVA$aov, "means", se = TRUE)
```

```{r, message=FALSE,waring=FALSE}
d.f.temporal %>%
  filter(Subject != "s020") %>%
  group_by(Subject, StimulationProtocolID, Condition) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  ezPlot(
    data = .,
    dv = .(proportion),
    within = .(Condition, StimulationProtocolID),
    wid = .(Subject),
    x = .(StimulationProtocolID),
    split = .(Condition),
    levels = list(
        StimulationProtocolID = list(
            new_order = c('A','B'), 
            new_names = c('Stimulation','Sham')),
        Condition = list(
            new_order = c('allNeutral', 'halfEmotional'),
            new_names = c('All Neutral', 'Half Emotional')
        ))
  ) -> p
p +
  scale_y_continuous(limits = c(NA, NA)) +
  labs(title = "Temporal Contiguity",
       subtitle = "As a Function of List Composition and Stimulation",
       y = "Temporal Contiguity Score",
       x = "Stimulation",
       colour = "List Composition",
       shape = "List Composition",
       linetype = "List Composition")
ggsave(filename = "~/Desktop/TotoTDCS_Figure1.png")
```

# Exploratory

Lets explore!

## Time of Day

Recent work from Dave Gallo's lab suggests that the effect of tDCS may depend on **time of day**, whereby stimulation enhances memory primarily for participant who participate in the morning.

```{r}
d.f %>%
  group_by(Subject, TimeOfDay, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion)) %>%
  filter(!is.element(el = Subject, set = c("s024", "s032"))) -> tmp 

tmp %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, fill = NULL, color = StimulationProtocolID)) +
  facet_grid(~TimeOfDay) +
  stat_summary_bin(aes(group = Subject), geom = "line", fun.y = "mean") +
  stat_summary_bin(aes(group = Subject), geom = "point", fun.y = "mean") +
  stat_summary(geom = "crossbar", fun.data = "mean_se", width = .1) + 
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Proportion Recalled",
        subtitle = "By Protocol and Time of Day",
        x = "Protocol") -> Graph

# AM
tmp %>%
  filter(TimeOfDay == "AM") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult
  df <- testResult$parameter[["df"]]
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)

  AM_lab <- paste0("t(", df, ") =", t, ", p = ", p)
  
# PM
tmp %>%
  filter(TimeOfDay == "PM") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult
  df <- testResult$parameter[["df"]]
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)
  
  PM_lab <- paste0("t(", df, ") =", t, ", p = ", p)

d.f.annot <- data.frame(
  label = c(AM_lab, PM_lab),
  TimeOfDay = c("AM", "PM"),
  x = c(1.5, 1.5),
  y = c(1, 1)
)

Graph +
  geom_text(data = d.f.annot, mapping = aes(x = x, y = y, label = label, color = NULL))

```

There is no evidence supporting this idea in our data. Keep in mind, the N's in both AM and PM conditions are different, since this was not something we explicitly controlled for. Also, note that this analysis involved dropping subjects that performed sessions 1 and session 2 at different times of day (i.e., either AM-->PM or PM-->AM).  

```{r}
d.f.temporal %>%
  group_by(Subject, TimeOfDay, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) %>%
  filter(!is.element(el = Subject, set = c("s024", "s032"))) -> tmp 

tmp %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, fill = NULL, color = StimulationProtocolID)) +
  facet_grid(~TimeOfDay) +
  stat_summary_bin(aes(group = Subject), geom = "line", fun.y = "mean") +
  stat_summary_bin(aes(group = Subject), geom = "point", fun.y = "mean") +
  stat_summary(geom = "crossbar", fun.data = "mean_se", width = .1) + 
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Temporal Contiguity",
        subtitle = "By Protocol and Time Of Day",
        x = "Protocol") -> Graph

# AM
tmp %>%
  filter(TimeOfDay == "AM") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult
  df <- testResult$parameter[["df"]]
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)

  AM_lab <- paste0("t(", df, ") =", t, ", p = ", p)
  
# PM
tmp %>%
  filter(TimeOfDay == "PM") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = TRUE) -> testResult
  df <- testResult$parameter[["df"]]
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)
  
  PM_lab <- paste0("t(", df, ") =", t, ", p = ", p)

d.f.annot <- data.frame(
  label = c(AM_lab, PM_lab),
  TimeOfDay = c("AM", "PM"),
  x = c(1.5, 1.5),
  y = c(1, 1)
)

Graph +
  geom_text(data = d.f.annot, mapping = aes(x = x, y = y, label = label, color = NULL))

```

Samesies for temporal contiguity.  

## Counter Balance Breakup

Does stimulation interact with order?  

```{r}
d.f %>%
  group_by(Subject, sessionID, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion)) -> tmp 

tmp %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, fill = NULL, color = StimulationProtocolID)) +
  facet_grid(~sessionID) +
  geom_point(aes(color = NULL)) +
  stat_summary(geom = "crossbar", fun.data = "mean_se", width = .1) + 
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Proportion Recalled",
        subtitle = "By Protocol and Session Order",
        x = "Protocol") -> Graph

# AM
tmp %>%
  filter(sessionID == "ses-01") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = FALSE) -> testResult
  df <- round(testResult$parameter[["df"]], 2)
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)

  ses01_lab <- paste0("t(", df, ") = ", t, ", p = ", p)
  
# PM
tmp %>%
  filter(sessionID == "ses-02") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = FALSE) -> testResult
  df <- round(testResult$parameter[["df"]], 2)
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)
  
  ses02_lab <- paste0("t(", df, ") = ", t, ", p = ", p)

d.f.annot <- data.frame(
  label = c(ses01_lab, ses02_lab),
  sessionID = c("ses-01", "ses-02"),
  x = c(1.5, 1.5),
  y = c(1, 1)
)

Graph +
  geom_text(data = d.f.annot, mapping = aes(x = x, y = y, label = label, color = NULL))
```

```{r}
d.f.temporal %>%
  group_by(Subject, sessionID, StimulationProtocolID) %>%
  summarise(proportion = mean(proportion, na.rm = TRUE)) -> tmp 

tmp %>%
  ggplot(aes(x = StimulationProtocolID, y = proportion, fill = NULL, color = StimulationProtocolID)) +
  facet_grid(~sessionID) +
  geom_point(aes(color = NULL)) +
  stat_summary(geom = "crossbar", fun.data = "mean_se", width = .1) + 
  scale_fill_discrete(guide = FALSE) +
  labs(title = "Temporal Contiguity",
        subtitle = "By Protocol and Session Order",
        x = "Protocol") -> Graph

# AM
tmp %>%
  filter(sessionID == "ses-01") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = FALSE) -> testResult
  df <- round(testResult$parameter[["df"]], 2)
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)

  ses01_lab <- paste0("t(", df, ") = ", t, ", p = ", p)
  
# PM
tmp %>%
  filter(sessionID == "ses-02") %>%
  t.test(proportion ~ StimulationProtocolID, data = ., paired = FALSE) -> testResult
  df <- round(testResult$parameter[["df"]], 2)
  t  <- round(testResult$statistic, 2)
  p  <- round(testResult$p.value, 2)
  
  ses02_lab <- paste0("t(", df, ") = ", t, ", p = ", p)

d.f.annot <- data.frame(
  label = c(ses01_lab, ses02_lab),
  sessionID = c("ses-01", "ses-02"),
  x = c(1.5, 1.5),
  y = c(1, 1)
)

Graph +
  geom_text(data = d.f.annot, mapping = aes(x = x, y = y, label = label, color = NULL))
```

No, it does not seem to.  

## Emotional Words

First, Score Each Word as recalled or not:

```{r}
# Score Each Word as recalled or not

study$recalled <- FALSE

for(ses in unique(study$sessionID)){
  for(s in unique(study$subjectID)){
     for(l in unique(study$listID)){
        
       # Filter Session & Filter Subject & Filter List
       Fses <- recall$sessionID == ses
       FS <- recall$subjectID == s
       FL <- recall$listID == l
       curScurL_recall <- recall[FL & FS & Fses,]

       # Filter Session & Filter Subject & Filter List
       Fses <- study$sessionID == ses
       FS <- study$subjectID == s
       FL <- study$listID == l
       curScurL_study  <- study[FL & FS & Fses,]       
              
       # Loop over words
       for(w in curScurL_study$Word){
         Fw <- study$Word == w
         study$recalled[Fses & FS & FL & Fw] <- any(grepl(pattern = w, x = curScurL_recall$emily, ignore.case = TRUE))
       }
    } 
  }
}

```

Are emotional words more likely to be recalled than neutral words in the `halfEmotional` condition? Is this _at_ _the_ _expense_ _of_ Neutral Words in this condition?  

Lets run an ANOVA to find out.  

A table:  

```{r}
(study %>%
  group_by(subjectID, EmotionCategory, Condition) %>%
  summarize(proportion = mean(recalled)) %>% 
  unite(col = "Category", Condition, EmotionCategory, sep = "-") -> PropRecalledByEmotion)
```

A figure:  

```{r, warning=FALSE}
defaultColors <- hue_pal()(3)

# ANOVA
ezANOVA(PropRecalledByEmotion, dv = proportion, wid = subjectID, within = Category) -> ANOVA

DFd <- ANOVA$ANOVA$DFn
DFn <- ANOVA$ANOVA$DFd
F   <- round(ANOVA$ANOVA$F, 2)
p   <- round(ANOVA$ANOVA$p, 2)

PropRecalledByEmotion %>%
  ggplot(aes(x = Category, y = proportion, group = subjectID)) +
  geom_point() +
  stat_summary(aes(group = NULL, color = Category), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  annotate(geom = "text", 
           x = 2, 
           y = 1, 
           label = paste0("F(", DFd, ",", DFn, ") =", F, ", p = ", p)) +
  theme_grey() +
  scale_y_continuous(limits = c(0,NA)) + 
  labs(title = "Proportion Recalled",
       subtitle = "By Valence and Condition",
       y = "Proportion",
       x = "Condition-Valence")
```

The results of the ANOVA allows us to reject the null hypothesis that all three of our conditions are equal.  

Follow-up hypothesis tests #1

Are emotional words remembered better than neutral words in the halfEmotional condition?

A table:

```{r}
(study %>%
  filter(Condition == "halfEmotional") %>%
  group_by(subjectID, EmotionCategory, Condition) %>%
  summarize(proportion = mean(recalled)) %>%
  unite(col = "Category", Condition, EmotionCategory, sep = "-") -> PropRecalledByEmotion)
```

A figure:

```{r}
PropRecalledByEmotion %>%
  t.test(proportion ~ Category, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 3)

PropRecalledByEmotion %>%
  ggplot(aes(x = Category, y = proportion, group = subjectID)) +
  geom_point() +
  geom_line() +
  stat_summary(aes(group = NULL, color = Category), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  scale_y_continuous(limits = c(0,NA)) + 
  labs(title = "Proportion Recalled",
       subtitle = "Half-Emotional Condition Only",
       y = "Proportion",
       x = "Category-Valence") +
  scale_color_manual(values = defaultColors[c(2,3)]) 
  
```

Are emotional words more likely to be recalled than neutral words in the `halfEmotional` condition? - **YES!!**

Follow-up hypothesis tests #2

Is this at the expense of neutral words?

A table:

```{r}
(study %>%
  filter(EmotionCategory == "Neutral") %>%
  group_by(subjectID, EmotionCategory, Condition) %>%
  summarize(proportion = mean(recalled)) %>%
  unite(col = "Category", Condition, EmotionCategory, sep = "-") -> PropRecalledByEmotion)
```

A figure:

```{r}
PropRecalledByEmotion %>%
  t.test(proportion ~ Category, data = ., paired = TRUE) -> testResult

df <- testResult$parameter[["df"]]
t  <- round(testResult$statistic, 2)
p  <- round(testResult$p.value, 3)

PropRecalledByEmotion %>%
  ggplot(aes(x = Category, y = proportion, group = subjectID)) +
  geom_point() +
  geom_line() +
  stat_summary(aes(group = NULL, color = Category), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  annotate(geom = "text", 
           x = 1.5, 
           y = 1, 
           label = paste0("t(", df, ") =", t, ", p = ", p)) +
  theme_grey() +
  scale_y_continuous(limits = c(0,NA)) + 
  labs(title = "Proportion Recalled",
       subtitle = "Neutral Words Only",
       y = "Proportion",
       x = "Condition-Valence") +
  scale_color_manual(values = defaultColors[c(1,3)]) 
  
```

Is this at the expense of Neutral words? - **YES!!** ...depending on how you feel about p < .05 :/  

### Does stimulation moderate this effect?

Does stimulation moderate this effect? Lets run an ANOVA and find out.  

```{r, warning=FALSE}
(study %>%
  left_join(subjectIDs_df, by = c("subjectID" = "SubjectID", "sessionID" = "Session")) %>%
  group_by(subjectID, StimulationProtocolID, EmotionCategory, Condition) %>%
  summarize(proportion = mean(recalled)) %>% 
  unite(col = "Category", Condition, EmotionCategory, sep = "-") -> PropRecalledByEmotion)
```

```{r}
PropRecalledByEmotion %>%
  ggplot(aes(x = Category, y = proportion, group = subjectID)) +
  facet_grid(.~StimulationProtocolID) +
  geom_point() +
  stat_summary(aes(group = NULL, color = Category), 
               geom = "crossbar", 
               width = .2, 
               fun.data = "mean_se") +
  theme_grey() +
  scale_y_continuous(limits = c(0,NA)) + 
  labs(title = "Proportion Recalled",
       subtitle = "By Stimulation Protocol",
       y = "Proportion",
       x = "",
       color = "Condition-Valuence") +
  theme(axis.text.x = element_blank())
```

```{r, warning = FALSE}
# ANOVA
ezANOVA(PropRecalledByEmotion, dv = proportion, wid = subjectID, within = .(Category, StimulationProtocolID))
```

Does stimulation moderate this effect? - **No**.

# EEG Data Check

Describe Data

```{r}
FullPath <- list.files(path = "/Volumes/GoogleDrive/My Drive/Behavioral Data/TOTO-tDCS", 
                       recursive = TRUE, 
                       full.names = TRUE,
                       pattern = "\\.[ein][ane][sfd][yof]")
Path     <- as.character(lapply(X = FullPath, FUN = dirname))
FileName <- as.character(lapply(X = FullPath, FUN = basename))
DateTime <- regmatches(m = regexpr(text = FullPath, 
                                   pattern = "(?<=\\/)[0-9]*(?=_)", 
                                   perl = TRUE), 
                       x = FullPath)
subject  <- regmatches(m = regexpr(text = FullPath, 
                                   pattern = "s[0-9]{3}", 
                                   perl = TRUE), 
                       x = FullPath)
session  <- regmatches(m = regexpr(text = FullPath, 
                                   pattern = "ses-0[12]",
                                   perl = TRUE),
                       x = FullPath)
Task     <- regmatches(m = regexpr(text = FullPath, 
                                   pattern = "(?<=_)[a-zA-Z ]*(?=\\.)",
                                   perl = TRUE),
                       x = FullPath)
Ext      <- regmatches(m = regexpr(text = FullPath, 
                                   pattern = "\\..*$",
                                   perl = TRUE),
                       x = FullPath)
eegdata <- data.frame(FullPath = FullPath, 
                      Path = Path, 
                      FileName = FileName, 
                      DateTime = DateTime, 
                      subject = subject, 
                      session = session, 
                      Task = Task, 
                      Ext = Ext)
```

Which datasets have Marker codes?

```{r}
eegdata %>%
  filter(grepl(x = Ext, pattern = "\\.easy")) %>%
  complete(subject, session) -> ERE

ERE$hasAnyEEGcodes <- NA
ERE$hasAllEEGcodes <- NA

data <- vector(mode = "list", length = nrow(ERE))

for(i in 1:nrow(ERE)){
  if(!is.na(ERE$FullPath[[i]])){
    print(i)
    data[[i]] <- read.table(as.character(ERE$FullPath[[i]]))
  }
}

for(i in 1:length(data)){
  if(is.null(data[[i]])){
  } else{
    ERE$hasAnyEEGcodes[[i]] <- length(unique(data[[i]]$V12)) > 1
    ERE$hasAllEEGcodes[[i]] <- all(is.element(c(1, 99), unique(data[[i]]$V12)))
  }
}
```

A Table:

```{r}
ERE %>%
  filter(!is.element(subject, c("s004", "s025"))) 
```

How many EEG data sets do we have with Any EEG codes?

```{r}
ERE %>%
  filter(!is.element(subject, c("s004", "s025"))) %>%
  count(hasAnyEEGcodes)
```

How many EEG data sets do we have with Any EEG codes? *n* *=* *36*

```{r}
ERE %>%
  filter(!is.element(subject, c("s004", "s025"))) %>%
  count(hasAllEEGcodes)
```

How many EEG datasets do we have with All EEG codes? *n* *=* *21*

```{r}
ERE %>%
  filter(!is.element(subject, c("s004", "s025"))) %>%
  select(subject, session, hasAnyEEGcodes) %>%
  spread(session, hasAnyEEGcodes) %>%
  mutate(BothSessionsHaveEEGdataWithCodes = `ses-01` & `ses-02`)
```

How many EEG data sets do we have that have EEG codes in both sessions?

```{r}
ERE %>%
  filter(!is.element(subject, c("s004", "s025"))) %>%
  select(subject, session, hasAnyEEGcodes) %>%
  spread(session, hasAnyEEGcodes) %>%
  mutate(BothSessionsHaveEEGdataWithCodes = `ses-01` & `ses-02`) %>%
  count(BothSessionsHaveEEGdataWithCodes)
```

How many EEG data sets do we have that have EEG codes in both sessions? *n* *=* *10*